%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Online Pong Experience for Endless Fun and Friendly Competition} % Job title
    {OverPing} % Organization
    {1337, benguerir} % Location
    {Aug. 2023 - Dec. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {a single web application as an online pong game, where users can play,
chat, create channels, and all the other functional features like
updating profile, send/receive friend request, block/unblock user.}
        \item {In my role as a front-end developer, I used React with TypeScript to
improve the code integrity.}
        \item {Embracing the Clean Architecture
principles and following the MVVM pattern, I aimed for a structured
and maintainable codebase.}
        \item {I utilized Tailwind CSS and
Styled Components with Twin Micro for efficient styling.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Unveiling the Art of HTTP Server} % Job title
    {HTTP web server} % Organization
    {1337, benguerir} % Location
    {May. 2023 - Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {a simple a http server like nginx that store, process, and deliver web
pages to clients via http, it is capable of handling GET/POST/DELETE
request.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Where keystrokes meet magic: Breathing life into systems with command lines} % Job title
    {Minishell} % Organization
    {1337, benguerir} % Location
    {Mar. 2022 - May. Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {a simple like bash program that communicate with the kernel using
interactive lines of commands like : cd, ls , and the most loved one git}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {intro to system administration} % Job title
    {Inception} % Organization
   {1337, benguerir} % Location
    {Mar. 2023 - May. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {In this project i create custom docker images for WordPress website
from scratch and virtualize them. this enable me to explore the world
of system administration.}
      \end{cvitems}
    }



%---------------------------------------------------------
\end{cventries}
